Supplemental Materials, Methods and Results

### 2021-04-23 ms.Rmd
MS udpated now to include predators

# Display dl
    ConspicDisplayAC <- lmer(dL ~ sc_SVL + Population + (1|ID), data=Display_1)
    summary(ConspicDisplayAC)
    CI_AC_display <- data.frame(confint(ConspicDisplayAC))
    anovaConspicDisplayAC <- anova(ConspicDisplayAC)

@@

# Courtship dl
ConspicCourtshipAC <- lmer(dL ~ sc_SVL + Population  + (1|ID), data=Courtship)
summary(ConspicCourtshipAC)
CI_AC_court <- data.frame(confint(ConspicCourtshipAC))
courship_anovaAC <- anova(ConspicCourtshipAC)

# Courtship dS
  ConspicCourtshipCC <- lmer(dS ~ sc_SVL + Population  + (1|ID), data=Courtship)
 courship_anovaCC <- anova(ConspicCourtshipCC)
```

@@

We manipulated both the social and predatory context chameleons encountered, in both their native Kenyan range and their introduced Hawaiian range, to test three hypotheses about colour signal evolution. Using spectrophotometry and visual modelling that relied on our understanding of the chameleon visual system we quntified chromatic and achromatic contrast against the backgrounds in each environment (i.e., leaves and stems in Kenya and Hawaii).

Sexual selection is expected to favour more conspicuous dymamic sexual signals in Hawaii under relaxed predation because higher predation should favour cryptic signals. In support of this prediction, male display colouration exhibited in social contexts (i.e., male-male contests and courtship) was more conspicuous to a conspecific in Hawaii compared with Kenya (**Male-Male Contests**: Acromatic contrast ($dl$); $F_{`r anovaConspicDisplayAC$NumDF[2]`,`r anovaConspicDisplayAC$DenDF[2]`}$ = `r anovaConspicDisplayAC[5][2,]`, p = `r p_value(anovaConspicDisplayAC[6][2,])`; Chromatic contrast ($dS$): $F_{`r anovaConspicDisplayCC$NumDF[2]`,`r anovaConspicDisplayCC$DenDF[2]`}$ = `r anovaConspicDisplayCC[5][2,]`, p = `r p_value(anovaConspicDisplayCC[6][2,])`; **Courtship displays**: Acromatic contrast ($dl$); $F_{`r courship_anovaAC$NumDF[2]`,`r courship_anovaAC$DenDF[2]`}$ = `r courship_anovaAC[5][2,]`, p = `r p_value(courship_anovaAC[6][2,])`; Chromatic contrast ($dS$): $F_{`r courship_anovaCC$NumDF[2]`,`r courship_anovaCC$DenDF[2]`}$ = `r courship_anovaCC[5][2,]`, p = `r p_value(courship_anovaCC[6][2,])`), and this was  true across all body regions measured (See Supplemental Materials, table S1). Overall, Kenyan chameleons were significantly more crypic compared to introduced Hawaiian counterparts (Acromatic Contrast between Hawaiian and Kenyan Populations, Male-male contests: $\beta$ = `r fixef(ConspicDisplayAC)[3]`, 95% CI = `r CI_AC_display[5,1]` to  `r CI_AC_display[5,2]`, df = `r summary(ConspicDisplayAC)$coefficients[3, "df"]`, t =  `r summary(ConspicDisplayAC)$coefficients[3, "t value"]`, p = `r p_value(summary(ConspicDisplayAC)$coefficients[3, "Pr(>|t|)"])`, Courtship: $\beta$ = `r fixef(ConspicCourtshipAC)[3]`, 95% CI = `r CI_AC_court[5,1]` to  `r CI_AC_court[5,2]`, df = `r summary(ConspicCourtshipAC)$coefficients[3, "df"]`, t =  `r summary(ConspicCourtshipAC)$coefficients[3, "t value"]`, p = `r p_value(summary(ConspicCourtshipAC)$coefficients[3, "Pr(>|t|)"])`, see figure 1a & b).

Sexual signals are expected to be detected much more easily by predators (ie., snakes and birds) in Hawaii as a result of reduced predation. In support of this prediction, Hawaiian chameleons were significantly more conspicous to both snake and bird predators (figure 1b & c).

```{r Figure1, fig.width = 15, fig.height= 9.287443, fig.cap= "Chromatic and achromatic contrast in Just Noticiable Differences (JND), of Hawaiian and Kenyan chameleons against their respective backgrounds (i.e., average environment of stems and leaves). A & B) Contrast of male chameleons during male-male contests and courtship. JNDs are calculated based on the chameleon visual system. 'NS' denotes non-significant contasts, whereas '**' indicates significant differences < 0.001.}
## Make figures that average across body regions, but display Social Context

@@

# Now calculate the averages for each population anc Colour (i.e., context)

@@

males <- readPNG("./photos/male_fight.png", native = TRUE)
#males <- image_scale(males, "200x200")

females <- readPNG("./photos/courtship.png", native = TRUE)
#females <- image_scale(females, "200x200")

p1 <- ggplot(summary_data, aes(x = Population, y = Mean_dS, group = Colour, color = Colour)) +
    ylim(2.5, 6.5) + 
  geom_point(size = 3, position = position_dodge(width=0.5)) +
  geom_errorbar(aes(ymin = Lower_dS, ymax = Upper_dS), position = position_dodge(width=0.5), width = 0) + 
  geom_line(position = position_dodge(width=0.5)) + 
  scale_color_manual(values = wes_palette("Cavalcanti1")) + #Change color palette here see: https://github.com/karthik/wesanderson
  xlab("") + 
  ylab("Chromatic contrast (JND)") +
  annotate("segment", x = 0.85, xend = 1.85, y = 6.1, yend = 6.1, colour = "black") +
  annotate("segment", x = 1.12, xend = 2.12, y = 5.7, yend = 5.7, colour = "black") + 
  annotate("text", x = 0.85+(1.85-0.85)/2,  y = 6.2, label = "NS",  size = 6) + 
  annotate("text", x = 1.12+(2.12-1.12)/2, y = 5.8, label = "NS", size = 6) + 
  theme_bw() +
  labs(colour = "Social Context") +
  theme(legend.position = c(0.28, 0.08),
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    axis.text=element_text(size=18),
    axis.title=element_text(size=20,face="bold"),
    legend.text =element_text(size = 12),
    legend.title =element_text(size = 12, face = "bold")) +
   inset_element(males,
                left = 0.45,
                right = 0.90,
                bottom = 0.58,
                top = 0.75, ignore_tag = TRUE) + 
    inset_element(females,
                left = 0.30,
                right = 0.75,
                bottom = 0.15,
                top = 0.28, ignore_tag = TRUE) 
      #annotation_raster(males, xmin = 1.2, xmax = 1.9, ymin = 4.8, ymax = 5.3) + 
      #annotation_raster(females, xmin = 1, xmax = 1.7, ymin = 3.5, ymax = 4)

@@

plot_grid(p1, p2, labels = c("A", "B"), label_size = 16,
  label_fontface = "bold", rel_widths=c(1,1))

>>>>

# Display dl
    ConspicDisplayAC <- lmer(dL ~ sc_SVL + Population + (1|ID), data=Display_1)
    summary(ConspicDisplayAC)
    coefAIC_display = fixef(ConspicDisplayAC)[3]
    CI_AC_display <- data.frame(confint(ConspicDisplayAC))
    anovaConspicDisplayAC <- anova(ConspicDisplayAC)

@@

# Courtship dl
ConspicCourtshipAC <- lmer(dL ~ sc_SVL + Population  + (1|ID), data=Courtship)
summary(ConspicCourtshipAC)
coefAIC_court = fixef(ConspicCourtshipAC)[3]
CI_AC_court <- data.frame(confint(ConspicCourtshipAC))
courship_anovaAC <- anova(ConspicCourtshipAC)

# Courtship dS
  ConspicCourtshipCC <- lmer(dS ~ sc_SVL + Population  + (1|ID), data=Courtship)
 courship_anovaCC <- anova(ConspicCourtshipCC)

 #########################################################
# Displays to Predators, birds and snake
#########################################################
 Predator <- read.table("./data/Predator_2_3.csv", 
                       header=TRUE, sep=",", dec=".", strip.white=TRUE)

# Clean up
 Predator <- Predator %>% filter(!BodyRegion == "botflank" & !BodyRegion =='gularbot') %>% as.data.frame() #exclude bottom flank.
Predator$BodyRegion <- factor(Predator$BodyRegion) #updates levels for the variable BodyRegion

# Transformation
Predator <- Predator %>% mutate(log_dS = log(dS),
                                log_dL = log(dL),
                                sqrt_dS = sqrt(dS),
                                sqrt_dL = sqrt(dL))

# Models - Achromatic Contrast (dL)

# First, if predator type varies across populations then we would predcit that whether snake and bird actually are different would depend on the population. For example, if, say, in HAwaii and Kenya birds were equally likely as predators then dL would not vary for birds across populations, but would so for snakes. This is an interaction.

PredatorAC <- lmer(dL ~ Predator + Population + Predator:Population + (1|ID), data = Predator) 
summary(PredatorAC)
anova_predators_inter <- anova(PredatorAC)

# No support for an interaction, so can drop interaction. Tells us that predation, regardless of whether we are talking snake or bird is just low in Hawaii, otherwise, we would predict that signals would evolve to match the predatory system 
PredatorAC <- lmer(dL ~ Predator + Population + (1|ID), data = Predator) 
summary(PredatorAC)
anova_predators <- anova(PredatorAC)

# Chromatic contrast - dS

PredatorCC <- lmer(dS ~ Predator + Population + Predator:Population + (1|ID), data = Predator) 
summary(PredatorCC)
anova_predators_interCC <- anova(PredatorCC)

Predator$pred_pop <- with(Predator, interaction(Predator, Population))
PredatorCC_pred_pop <- lmer(dS ~ pred_pop + (1|ID), data = Predator) 
summary(PredatorCC_pred_pop)

hypthesis_test <- glht(PredatorCC_pred_pop, df = 101, # df to get t-distribution, use number of lizards not data points
             linfct = mcp(pred_pop = c("snake.Hawaii - snake.Kenya = 0",
                                       "bird.Hawaii  - bird.Kenya = 0",
                                       "snake.Hawaii - bird.Hawaii = 0",
                                       "snake.Kenya  - bird.Kenya = 0")))
summary(hypthesis_test)
CI_hyp_test <- as.data.frame(confint(hypthesis_test)$confint)

@@

We manipulated both the social and predatory context chameleons encountered, in both their native Kenyan range and their introduced Hawaiian range, to test three hypotheses about colour signal evolution. Using spectrophotometry and visual modelling that relied on our understanding of the known chameleon visual system we quntified chromatic and achromatic contrast against the backgrounds in each environment (i.e., leaves and stems in Kenya and Hawaii).

Sexual selection is expected to favour more conspicuous dymamic sexual signals in Hawaii under relaxed predation because higher predation should favour cryptic signals whereas greater conspicuousness of sexual signals should be selected in social contexts. In support of this prediction, male display colouration exhibited in social contexts (i.e., male-male contests and courtship) was more conspicuous to a conspecific in Hawaii compared with Kenya (**Male-Male Contests**: Acromatic contrast ($dl$); $F_{`r anovaConspicDisplayAC$NumDF[2]`,`r anovaConspicDisplayAC$DenDF[2]`}$ = `r anovaConspicDisplayAC[5][2,]`, p = `r p_value(anovaConspicDisplayAC[6][2,])`; Chromatic contrast ($dS$): $F_{`r anovaConspicDisplayCC$NumDF[2]`,`r anovaConspicDisplayCC$DenDF[2]`}$ = `r anovaConspicDisplayCC[5][2,]`, p = `r p_value(anovaConspicDisplayCC[6][2,])`; **Courtship displays**: Acromatic contrast ($dl$); $F_{`r courship_anovaAC$NumDF[2]`,`r courship_anovaAC$DenDF[2]`}$ = `r courship_anovaAC[5][2,]`, p = `r p_value(courship_anovaAC[6][2,])`; Chromatic contrast ($dS$): $F_{`r courship_anovaCC$NumDF[2]`,`r courship_anovaCC$DenDF[2]`}$ = `r courship_anovaCC[5][2,]`, p = `r p_value(courship_anovaCC[6][2,])`), and this was  true across all body regions measured (See Supplemental Materials, table S1). Kenyan chameleons were significantly more crypic compared to introduced Hawaiian counterparts (Acromatic Contrast between Hawaiian and Kenyan Populations, Male-male contests: $\beta$ = `r coefAIC_display`, 95% CI = `r CI_AC_display[5,1]` to  `r CI_AC_display[5,2]`, df = `r summary(ConspicDisplayAC)$coefficients[3, "df"]`, t =  `r summary(ConspicDisplayAC)$coefficients[3, "t value"]`, p = `r p_value(summary(ConspicDisplayAC)$coefficients[3, "Pr(>|t|)"])`, Courtship: $\beta$ = `r coefAIC_court`, 95% CI = `r CI_AC_court[5,1]` to  `r CI_AC_court[5,2]`, df = `r summary(ConspicCourtshipAC)$coefficients[3, "df"]`, t =  `r summary(ConspicCourtshipAC)$coefficients[3, "t value"]`, p = `r p_value(summary(ConspicCourtshipAC)$coefficients[3, "Pr(>|t|)"])`, see figure 1a & b).

As a consequence of signal release, sexual signals are expected to be more easily detected by predators (i.e., snakes and birds) in Hawaii. Differential predation pressure resulting from snake and bird predation varying would also result in populations varying in their conspicuousness to different predators.  In support of these predictions, Hawaiian chameleons were significantly more conspicous to both snake and bird predators (figure 1b & c; Achromatic Contrast: ($dl$); $F_{`r anova_predators$NumDF[2]`,`r anova_predators$DenDF[2]`}$ = `r anova_predators[5][2,]`, p = `r p_value(anova_predators[6][2,])`). Differences in chromatic contrast between populations, however,  depended on the predator (significant predator by population interaction: $F_{`r anova_predators_interCC$NumDF[3]`,`r anova_predators_interCC$DenDF[3]`}$ = `r anova_predators_interCC[5][3,]`, p = `r p_value(anova_predators_interCC[6][3,])`). Interestingly, Kenyan and Hawaiian lizards were equally detectable by snakes, but Kenyan chameleons were significantly more cryptic from birds compared to Hawaiian chamleons (figure 1c; Snakes (Hawaii-Kenya): `r CI_hyp_test[1,1]`, 95% CI = `r CI_hyp_test[1,2]` to `r CI_hyp_test[1,3]`, p = 1; Birds (Hawaii-Kenya): `r CI_hyp_test[2,1]`, 95% CI = `r CI_hyp_test[2,2]` to `r CI_hyp_test[2,3]`, p = < 0.001).

```{r Figure1, fig.width = 14, fig.height= 14, fig.cap= "Chromatic and achromatic contrast in Just Noticiable Differences (JND), of Hawaiian and Kenyan chameleons against their respective backgrounds (i.e., average environment of stems and leaves). A & B) Contrast of male chameleons during male-male contests and courtship. JNDs are calculated based on the chameleon visual system. NS denotes non-significant contasts, whereas astericks indicates significant differences is < 0.001."}
## Make figures that average across body regions, but display Social Context

@@

# Now calculate the averages for each population and Colour (i.e., context) / predation

summary_data_pred <- Predator %>%
                group_by(Predator, Population) %>%
                summarise( Mean_dS = mean(dS, na.rm = T), 
                             SE_dS = sd(dS)/sqrt(length(unique(ID))),
                             Upper_dS = Mean_dS + 1.96*SE_dS,
                             Lower_dS = Mean_dS - 1.96*SE_dS, 
                           Mean_dL = mean(dL, na.rm = T), 
                             SE_dL = sd(dL)/sqrt(length(unique(ID))),
                             Upper_dL = Mean_dL + 1.96*SE_dL,
                             Lower_dL = Mean_dL - 1.96*SE_dL)

@@

#Grab photos
  males <- readPNG("./photos/male_fight.png", native = TRUE)
females <- readPNG("./photos/courtship.png",  native = TRUE)
  snake <- readPNG("./photos/snake_cham.png", native = TRUE)
   bird <- readPNG("./photos/bird_cham.png",  native = TRUE)

#plots
p1 <- ggplot(summary_data, aes(x = Population, y = Mean_dS, group = Colour, color = Colour)) +
    ylim(2.5, 6.5) + 
  geom_point(size = 3, position = position_dodge(width=0.5)) +
  geom_errorbar(aes(ymin = Lower_dS, ymax = Upper_dS), position = position_dodge(width=0.5), width = 0) + 
  geom_line(position = position_dodge(width=0.5)) + 
  scale_color_manual(values = wes_palette("Cavalcanti1")) + #Change color palette here see: https://github.com/karthik/wesanderson
  xlab("") + 
  ylab("Chromatic contrast (JND)") +
  annotate("segment", x = 0.85, xend = 1.85, y = 6.1, yend = 6.1, colour = "black") +
  annotate("segment", x = 1.12, xend = 2.12, y = 5.7, yend = 5.7, colour = "black") + 
  annotate("text", x = 0.85+(1.85-0.85)/2,  y = 6.2, label = "NS",  size = 6) + 
  annotate("text", x = 1.12+(2.12-1.12)/2, y = 5.8, label = "NS", size = 6) + 
  theme_bw() +
  labs(colour = "Social Context") +
  theme(legend.position = c(0.28, 0.08),
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    axis.text=element_text(size=18),
    axis.title=element_text(size=20,face="bold"),
    legend.text =element_text(size = 12),
    legend.title =element_text(size = 12, face = "bold")) +
   inset_element(males,
                left = 0.45,
                right = 0.90,
                bottom = 0.58,
                top = 0.75, ignore_tag = TRUE) + 
    inset_element(females,
                left = 0.30,
                right = 0.75,
                bottom = 0.15,
                top = 0.28, ignore_tag = TRUE) 
      #annotation_raster(males, xmin = 1.2, xmax = 1.9, ymin = 4.8, ymax = 5.3) + 
      #annotation_raster(females, xmin = 1, xmax = 1.7, ymin = 3.5, ymax = 4)

@@

p3 <- ggplot(summary_data_pred, aes(x = Population, y = Mean_dL, group = Predator, color = Predator)) +
  ylim(10, 30) + 
  geom_point(size = 3, position = position_dodge(width=0.5)) +
  geom_errorbar(aes(ymin = Lower_dL, ymax = Upper_dL), position = position_dodge(width=0.5), width = 0) + 
  geom_line(position = position_dodge(width=0.5)) + 
  scale_color_manual(values = wes_palette("Cavalcanti1")) + #Change color palette here see: https://github.com/karthik/wesanderson
  xlab("") + 
  ylab("Achromatic contrast (JND)") +
   annotate("segment", x = 0.90, xend = 1.90, y = 28, yend = 28, colour = "black") +
  annotate("segment", x = 1.12, xend = 2.12, y = 26, yend = 26, colour = "black") + 
  annotate("text", x = 0.9+((1.90 - 0.90)/2), y = 28.5, label = "**",  size = 6) + 
  annotate("text", x = 1.12+((2.12 - 1.12)/ 2), y = 26.5, label = "**", size = 6) + 
  theme_bw() +
  theme(legend.position = "none",
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    axis.text=element_text(size=18),
    axis.title=element_text(size=20,face="bold"),
    legend.text =element_text(size = 12),
    legend.title =element_text(size = 12, face = "bold")) +
    inset_element(snake,
                left = 0.45,
                right = 0.75,
                bottom = 0.60,
                top = 0.70, ignore_tag = TRUE) + 
    inset_element(bird,
                left = 0.05,
                right = 0.50,
                bottom = 0.25,
                top = 0.38, ignore_tag = TRUE)

p4 <- ggplot(summary_data_pred, aes(x = Population, y = Mean_dS, group = Predator, color = Predator)) +
  ylim(1, 9) + 
  geom_point(size = 3, position = position_dodge(width=0.5)) +
  geom_errorbar(aes(ymin = Lower_dS, ymax = Upper_dS), position = position_dodge(width=0.5), width = 0) + 
  geom_line(position = position_dodge(width=0.5)) + 
  scale_color_manual(values = wes_palette("Cavalcanti1")) + #Change color palette here see: https://github.com/karthik/wesanderson
  xlab("") + 
  ylab("Chromatic contrast (JND)") +
   annotate("segment", x = 0.88, xend = 1.88, y = 8.8, yend = 8.8, colour = "black") +
  annotate("segment", x = 1.12, xend = 2.12, y =2.5, yend = 2.5, colour = "black") + 
  annotate("text", x = 0.9+((1.90 - 0.90)/2), y = 8.9, label = "**",  size = 6) + 
  annotate("text", x = 1.12+((2.12 - 1.12)/ 2), y = 2.7, label = "NS", size = 6) + 
  theme_bw() +
  theme(legend.position = c(0.10, 0.08),
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    axis.text=element_text(size=18),
    axis.title=element_text(size=20,face="bold"),
    legend.text =element_text(size = 12),
    legend.title =element_text(size = 12, face = "bold")) +
    inset_element(bird,
                left = 0.30,
                right = 0.60,
                bottom = 0.45,
                top = 0.60, ignore_tag = TRUE) + 
    inset_element(snake,
                left = 0.02,
                right = 0.32,
                bottom = 0.20,
                top = 0.35, ignore_tag = TRUE)

plot_grid(p1, p2, p4, p3, labels = c("A", "B", "C", "D"), label_size = 16,
  label_fontface = "bold", rel_widths=c(1,1))

### 2021-04-23 supp.Rmd
MS udpated now to include predators

>>>>

#########################################################
# Displays to Predators, birds and snake
#########################################################
 Predator <- read.table("./data/Predator_2_3.csv", 
                       header=TRUE, sep=",", dec=".", strip.white=TRUE)

# Clean up
 Predator <- Predator %>% filter(!BodyRegion == "botflank" & !BodyRegion =='gularbot') %>% as.data.frame() #exclude bottom flank.
Predator$BodyRegion <- factor(Predator$BodyRegion) #updates levels for the variable BodyRegion

# Transformation, just in case residuals are non-normal they may help. Remember, models assume normality of residuals not normality of the data. None-normality could be driven by effects you wish to model. So, you need to account for these first.
Predator <- Predator %>% mutate(log_dS = log(dS),
                                log_dL = log(dL),
                                sqrt_dS = sqrt(dS),
                                sqrt_dL = sqrt(dL))

## Predator Model - Achromatic contrast (AC or dL)
## just this next section has Drew's code, which averages the backround (Leaf_B1, Leaf_B2, Leaf_T1, Leaf_T2, Stem1, Stem2) for each lizard body region measurement.
## This is the full model; however, we do not need background because the way the data is set up R is taking an average. See next model (background dropped)
PredatorAC <- lmer(dL ~ Predator + Population + BodyRegion + Background 
                         + Predator:Background + Predator:BodyRegion + (1|ID), data=Predator)
anova(PredatorAC)

# Posthoc tests
Predator$PopBRInt <- interaction(Predator$Population,Predator$BodyRegion)
PredatorAC2 <- lmer(sqrt_dL ~ PopBRInt + (1|ID), data=Predator)
summary(glht(PredatorAC2, linfct = mcp(PopBRInt = c("Hawaii.gular - Kenya.gular = 0",
                                                    "Hawaii.midflank - Kenya.midflank = 0", 
                                                    "Hawaii.topflank - Kenya.topflank = 0", 
                                                    "Hawaii.tailbase - Kenya.tailbase = 0" ))))
## dropping background from model (it is still averaged)
# anova gives us significance of fixed effects
# ranova tests random effects (note: report just LRT and df)
# need the SD of residuals and random effects from summary (just report random effects)

PredatorAC <- lmer(dL ~ Predator + Population + BodyRegion +  
                           + Population:BodyRegion + (1|ID), data= Predator) # we have gularbot for Kenya but not Hawaii, so exclude it
anova(PredatorAC)
ranova(PredatorAC)

#for random effects, use ranova (is variance > 0?) report just LRT and df and need the SD of residuals and random effects from summary (just report random effects)

Predator$PopBRInt <- interaction(Predator$Population,Predator$BodyRegion)
PredatorAC2 <- lmer(dL ~ PopBRInt + (1|ID), data=Predator)
summary(glht(PredatorAC2, linfct = mcp(PopBRInt = c("Hawaii.gular - Kenya.gular = 0",
                                                    "Hawaii.midflank - Kenya.midflank = 0", 
                                                    "Hawaii.topflank - Kenya.topflank = 0", 
                                                    "Hawaii.tailbase - Kenya.tailbase = 0" ))))

# Chromatic Contast - dS

## Predator Model - Chromatic contrast (CC or dS)
## just this next section has Drew's code, which averages the backround (Leaf_B1, Leaf_B2, Leaf_T1, Leaf_T2, Stem1, Stem2) for each lizard body region measurement.
## This is the full model; however, we do not need background because the way the data is set up R is taking an average. See next model (background dropped)
PredatorCC <- lmer(sqrt_dS ~ Predator + Population + BodyRegion + Background 
                   + Predator:Background + Predator:BodyRegion + (1|ID), data=Predator)
Predator$PopBRInt <- interaction(Predator$Population,Predator$BodyRegion)
PredatorCC2 <- lmer(sqrt_dS ~ PopBRInt + (1|ID), data=Predator)
summary(glht(PredatorCC2, linfct = mcp(PopBRInt = c("Hawaii.gular - Kenya.gular = 0","Hawaii.midflank - Kenya.midflank = 0", "Hawaii.topflank - Kenya.topflank = 0", 
                                                    "Hawaii.tailbase - Kenya.tailbase = 0" ))))

## dropping background from model (it is still averaged)
# anova gives us significance of fixed effects
# ranova tests random effects (note: report just LRT and df)
# need the SD of residuals and random effects from summary (just report random effects)

PredatorCC <- lmer(sqrt_dS ~ Predator + Population + BodyRegion +  
                     + Population:BodyRegion + (1|ID), data=Predator[Predator$BodyRegion!='gularbot',]) # we have gularbot for Kenya but not Hawaii, so exclude it
anova(PredatorCC)
ranova(PredatorCC)

### This is old code for when in the above model, predator was nonsignificant, so we can drop it from the model (below). But after sqrt it is significant, so don't use this code. Just keeping it in case.
PredatorCC <- lmer(sqrt_dS ~ Population + BodyRegion +  
                     + Population:BodyRegion + (1|ID), data=Predator[Predator$BodyRegion!='gularbot',]) # we have gularbot for Kenya but not Hawaii, so exclude it
anova(PredatorCC)
ranova(PredatorCC)
###

#for random effects, use ranova (is variance > 0?) report just LRT and df and need the SD of residuals and random effects from summary (just report random effects)

Predator$PopBRInt <- interaction(Predator$Population,Predator$BodyRegion)
PredatorCC2 <- lmer(sqrt_dS ~ PopBRInt + (1|ID), data=Predator[Predator$BodyRegion!='gularbot',])
summary(glht(PredatorCC2, linfct = mcp(PopBRInt = c("Hawaii.gular - Kenya.gular = 0","Hawaii.midflank - Kenya.midflank = 0", "Hawaii.topflank - Kenya.topflank = 0", 
                                                    "Hawaii.tailbase - Kenya.tailbase = 0" ))))
